Mtcars Dataset
=====================================
  
Column{.tabset}
-----------------------------------------------------------------------
  
### About Dataset
<center><h2><b>Mtcars Data Set</b></h2></center>
***
<br><br>
The <em><b>mtcars </b></em>data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

A data frame with 32 observations on <b>11 (numeric) variables</b>. <br><br>
<li> mpg	Miles/(US) gallon </li><br>
<li> cyl	Number of cylinders </li><br>
<li> disp	Displacement (cu.in.) </li><br>
<li> hp	Gross horsepower </li><br>
<li> drat	Rear axle ratio </li><br>
<li> wt	Weight (1000 lbs) </li><br>
<li> qsec	1/4 mile time </li><br>
<li> vs	Engine (0 = V-shaped, 1 = straight) </li><br>
<li> am	Transmission (0 = automatic, 1 = manual) </li><br>
<li> gear	Number of forward gears </li><br>
<li> carb	Number of carburetors </li>

### Histogram
  
```{r}
# include the module
library(ggplot2)
source("gernalise_hist.R")

# call the module
d <- datasets::mtcars
GeneralHistogramUI("Mtcars", d, "Mtcars")
callModule(GeneralHistogram, "Mtcars", d, "Mtcars",5)
```


### Line Graph

```{r}
source("gernalise_lineplot.R")

GeneralLinePlotUI("Mtcars", d, "Mtcars")
callModule(GeneralLinePlot, "Mtcars", d, "Mtcars",6)
```

### Scatter Plot

```{r}
# include the module
source("gernalise_scatterplot.R")

GeneralScatterPlotUI("Mtcars", d, "Mtcars")
callModule(GeneralScatterPlot, "Mtcars", d, "Mtcars",6)
```


### Boxplot
```{r}
#print("Hello World")
source("gernalise_boxplot.R")

GeneralLinePlotUI("Mtcars", d, "Mtcars")
callModule(GeneralLinePlot, "Mtcars", d, "Mtcars",6)
```
